
\cvsection{Publications}

% google scholar summary
{
\fontsize{11pt}{1em}\bodyfont\bfseries\aiGoogleScholarSquare\space
\fontsize{11pt}{1em}\bodyfont\bfseries\color{blue}
\href{https://scholar.google.com.au/citations?user=0ZZ8xGYAAAAJ&hl=en}{Google Scholar Citation Metrics}
}

% researchgate summary
{
\fontsize{11pt}{1em}\bodyfont\bfseries\aiResearchGateSquare\space
\fontsize{11pt}{1em}\bodyfont\bfseries\color{blue}
\href{https://www.researchgate.net/profile/Junli_Zhang6}{ResearchGate Profile}
}

%------------------------------------------------
\begin{cventries}

%------------------------------------------------
\cventry
{\textbf{2016}}
{}
{}
{}
{
\begin{cvitems}
\setlength\itemsep{0.5em}
	\item {Bulli, P., \textbf{J. Zhang}, S. Chao, X. Chen, and M. Pumphrey. 2016. Genetic architecture of resistance to stripe rust in a global winter wheat germplasm collection. G3 6(8): 2237–2253.}
	\item {Chen, J., M.J. Guttieri, \textbf{J. Zhang}, D. Hole, E. Souza, and B. Goates. 2016a. A novel QTL associated with dwarf bunt resistance in Idaho 444 winter wheat. Theor Appl Genet: 1–10.}
	\item {Chen, J., J. Wheeler, K. O’Brien, W. Zhao, N. Klassen, \textbf{J. Zhang}, B. Bowman, Y. Wang, C. Jackson, J.M. Marshall, and X.M. Chen. 2016b. Registration of “UI Platinum” Hard White Spring Wheat. Journal of Plant Registrations 10(1): 36–40.}
\end{cvitems}
}
%------------------------------------------------
\cventry
{\textbf{2015}}
{}
{}
{}
{
\begin{cvitems}
\setlength\itemsep{0.5em}
	\item {Bonman, J.M., E.M. Babiker, A. Cuesta-Marcos, K. Esvelt-Klos, G. Brown-Guedira, S. Chao, D. See, J. Chen, E. Akhunov, \textbf{J. Zhang}, H.E. Bockelman, and T.C. Gordon. 2015. Genetic diversity among wheat accessions from the USDA National Small Grains Collection. Crop Science 55(3): 1243–1253.}
	\item {Bowman, B.C., J. Chen, \textbf{J. Zhang}, J. Wheeler, Y. Wang, W. Zhao, S. Nayak, N. Heslot, H. Bockelman, and J.M. Bonman. 2015. Evaluating grain yield in spring wheat with canopy spectral reflectance. Crop Science 55(5): 1881–1890.}
	\item {Maccaferri, M., \textbf{J. Zhang}, P. Bulli, Z. Abate, S. Chao, D. Cantu, E. Bossolini, X. Chen, M. Pumphrey, and J. Dubcovsky. 2015. A genome-wide association study of resistance to stripe rust (\emph{Puccinia striiformis} f. sp. \emph{tritici}) in a worldwide collection of hexaploid spring wheat (\emph{Triticum aestivum} L.). G3 5(3): 449–465. (\textbf{First 3 authors contributed equally})}
\end{cvitems}
}
%------------------------------------------------
\cventry
{\textbf{2014}}
{}
{}
{}
{
\begin{cvitems}
\setlength\itemsep{0.5em}
	\item {\textbf{Zhang, J.}, J. Chen, B.C. Bowman, K. O’Brien, J.M. Marshall, and J.M. Bonman. 2014a. Association mapping of Hagberg falling number in hard white spring wheat. Crop Science 54(3): 1243–1252.}
	\item {\textbf{Zhang, J.}, J. Chen, C. Chu, W. Zhao, J. Wheeler, E.J. Souza, and R.S. Zemetra. 2014b. Genetic dissection of QTL associated with grain yield in diverse environments. Agronomy 4(4): 556–578.}
	\item {Chen, J., G. Hu, \textbf{J. Zhang}, C. Chu, and Y. Wu. 2014. Mapping of STS markers developed from drought tolerance candidate genes and preliminary analysis of their association with yield-related traits in common wheat (\emph{Triticum aestivum}). Cereal Research Communications 42(2): 199–208.}
\end{cvitems}
}
%------------------------------------------------
\cventry
{\textbf{2013}}
{}
{}
{}
{
\begin{cvitems}		
	\item {Chen, J., J. Wheeler, J. Clayton, W. Zhao, K. O’Brien, \textbf{J. Zhang}, C. Jackson, J.M. Marshall, B.D. Brown, K. Campbell, X.M. Chen, R. Zemetra, and E.J. Souza. 2013. Registration of “UI Stone” soft white spring wheat. Journal of Plant Registrations 7(3): 321–326.}
\end{cvitems}
}
%------------------------------------------------
\cventry
{\textbf{2011}}
{}
{}
{}
{
\begin{cvitems}
\setlength\itemsep{0.5em}
	\item {Li, P., J. Chen, P. Wu, \textbf{J. Zhang}, C. Chu, D. See, G. Brown-Guedira, R. Zemetra, and E. Souza. 2011. Quantitative trait loci analysis for the effect of \emph{Rht-B1} dwarfing gene on coleoptile length and seedling root length and number of bread wheat. Crop Sci. 51(6): 2561–2568.}
\end{cvitems}
}
%------------------------------------------------
\end{cventries}

